---
title: "BoxPlot for inspiration and expiration"
author: "Alona Ben-Tal, Yunjiao Wang, and Maria Leite"
date: "2/12/2019"
output: html_document
---

The matlab file  dataGenerator_for_BoxPlot.m generates all the data plotted below. 

### Varying c1 for 3-phase case
```{r c1_3phase, include=TRUE}
library(R.matlab)
# read the matlab file as a list
data <- readMat('AllData_varyingc1_totBreath.mat')

# convert it to data frame
data <- data.frame(data)
# change the column name
names(data)<-c('Signal_period', 'Type', 'Duration')

data$Signal_period <- factor(data$Signal_period)
data$Type <- factor(data$Type)

library(ggplot2)

p = ggplot(data = data, aes(x = Signal_period, y = Duration)) +
  geom_boxplot(aes(fill = Type), width = 0.8) + theme_bw() +
  ggtitle("expiration(0), inspiration(1) and total breathing(2):varing p1 (phase3) ")
print(p)

```

### Varying c1 in 2-phase case

```{r c1_2phase, include=TRUE}
library(R.matlab)
# read the matlab file as a list
data <- readMat('AllData_varyingc1_totBreath1_phase2.mat')

# convert it to data frame
data <- data.frame(data)
# change the column name
names(data)<-c('Signal_period', 'Type', 'Duration')

data$Signal_period <- factor(data$Signal_period)
data$Type <- factor(data$Type)

library(ggplot2)

p = ggplot(data = data, aes(x = Signal_period, y = Duration)) +
  geom_boxplot(aes(fill = Type), width = 0.8) + theme_bw() +
  ggtitle("expiration(0), inspiration(1) and total breathing(2):varing p1 (phase2) ")
print(p)

```

### Varying c3 in 2-phase
```{r c3_2phase, include=TRUE}
library(R.matlab)
# read the matlab file as a list
data <- readMat('VaryingC3_Phase_2.mat')

# convert it to data frame
data <- data.frame(data)
# change the column name
names(data)<-c('Signal_period', 'Type', 'Duration')

data$Signal_period <- factor(data$Signal_period)
data$Type <- factor(data$Type)

library(ggplot2)

p = ggplot(data = data, aes(x = Signal_period, y = Duration)) +
  geom_boxplot(aes(fill = Type), width = 0.8) + theme_bw() +
  ggtitle("expiration(0), inspiration(1) and total breathing(2):varing p3 (phase2) ")
print(p)

```
Here the coloring is not missing. We cannot see color because of the thin boxes: the boxes along the slant line are in cyan and the boxes along the horizontal line are in red. 

See the magnified portion below.

```{r c3_2phase_enlarged, include=TRUE,echo=FALSE}
library(R.matlab)
# read the matlab file as a list
data <- readMat('VaryingC3_Phase_2.mat')

# convert it to data frame
data <- data.frame(data)
# change the column name
names(data)<-c('Signal_period', 'Type', 'Duration')
data<- subset(data,Signal_period < 130 )
data$Signal_period <- factor(data$Signal_period)
data$Type <- factor(data$Type)

library(ggplot2)

p = ggplot(data = data, aes(x = Signal_period, y = Duration)) +
  geom_boxplot(aes(fill = Type), width = 0.8) + theme_bw() +
  ggtitle("expiration(0), inspiration(1) and total breathing(2):varing p3 (phase2) ")
print(p)

```

### Varying c4 in 3-phase
```{r c4_3phase, include=TRUE}
library(R.matlab)
# read the matlab file as a list
data <- readMat('AllData_varyingc4_p3_121.mat')

# convert it to data frame
data <- data.frame(data)
# change the column name
names(data)<-c('Signal_period', 'Type', 'Duration')

data$Signal_period <- factor(data$Signal_period)
data$Type <- factor(data$Type)

library(ggplot2)

p = ggplot(data = data, aes(x = Signal_period, y = Duration)) +
  geom_boxplot(aes(fill = Type), width = 0.8) + theme_bw() +
  ggtitle("expiration(0), inspiration(1) and total breathing(2):varing p4 (phase3) ")
print(p)

```

### Varying c3 in 3-phase
```{r c3_3phase, include=TRUE}
library(R.matlab)
# read the matlab file as a list
data <- readMat('VaryingC3_Phase_3.mat')

# convert it to data frame
data <- data.frame(data)
# change the column name
names(data)<-c('Signal_period', 'Type', 'Duration')

data$Signal_period <- factor(data$Signal_period)
data$Type <- factor(data$Type)

library(ggplot2)

p = ggplot(data = data, aes(x = Signal_period, y = Duration)) +
  geom_boxplot(aes(fill = Type), width = 0.8) + theme_bw() +
  ggtitle("expiration(0), inspiration(1) and total breathing(2):varing p3 (phase3) ")
print(p)

```